Update of the ozone dry deposition in the OsloCTM3 v1.0

### 2018-11-07 DryDep.tex
Included table with simulation specifications and wrote some words about it. Need to make the diff plot, though.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%      
\section{Evaluation}
\label{sec:eval}
For meteorological input, we use \href{https://www.ecmwf.int/en/forecasts/documentation-and-support/evolution-ifs/cycle-38r1-summary-changes}{ECMWF - OpenIFS version cy38r1nc4}. CEDS historical emission inventory is used for emissions.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Sensitivity tests}
\label{subsec:sens}
Include table of all sensitivity runs.
\citep[e.g., $v^\chem{O_3}_\text{ice/snow} = 1/10000\,\unit{cm\,s^{-1}}$,][]{ACP:Helmig2007}
dry dep velocity over water \citep{JGR:Helmig2012} Impact of ocean? Although it is a low number there is 2\/3 ocean on earth... (Think, I read this in Hardacre paper... -> Luhar)

\begin{figure}[t]
  \includegraphics[width=8.3cm]{pictures/final-ozone_diff_maps}
  \caption{Relative difference between the sensitivity simulation emep\_psgsssh and the Wesely scheme in (a) surface ozone concentration; (b) ozone dry deposition velosity; (c) amount of ozone removed from the atmosphere by dry deposition.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparison with recent multi-model comparison}
\label{subsec:model}
Compare to \citet{ACP:Hardacre2015} as well as \citet{ACP:Luhar2017}. \citep{AE:Derwent2018} Uncertainties in surface ozone sources and sinks larger than in formulations? -> Need to read this one...
\begin{figure*}[t]
  \includegraphics[width=12cm]{pictures/final-total_ozone_drydep}\\
  \includegraphics[width=12cm]{pictures/final-total_ozone_drydepvelo}
  \caption{Comparison of various model runs with the OsloCTM3 and the multi-model-mean results by \citet{ACP:Hardacre2015}. (a) total annual ozone drydeposition; (b) annual average ozone dry depositon velocity.}
\end{figure*}
%
\begin{figure}[t]
  \includegraphics[width=8.3cm]{pictures/final-total_ozone_drydep_hem}
  \caption{Seasonal cycle of total amount of ozone removed from the atmosphere through dry deposition seperated into northern hemisphere (NH), tropics (TR), and southern hemisphere (SH). Comparison with results from \citet{ACP:Hardacre2015}.}
\end{figure}
%
\begin{figure}[t]
  \includegraphics[width=8.3cm]{pictures/final-total_ozone_drydep_monthly}\\
  \includegraphics[width=8.3cm]{pictures/final-total_ozone_drydepvelo_monthly}
  \caption{Comparison of monthly zonal distributions to results from \citep{ACP:Hardacre2015}. (a) Total amount of ozone removed from the atmosphere; (b) average ozone dry deposition velocitys.}
\end{figure}
%
\begin{figure}[t]
  \includegraphics[width=8.3cm]{pictures/final-total_ozone_drydepvelo_monthly_pft_nh}
  \caption{Average ozone dry deposition velocitys seperated by land use type and compared to results from \citep{ACP:Hardacre2015}.}
\end{figure}

@@

\begin{acknowledgements}
  This work was supported by the Norwegian Research Council (NRC) through the project The double punch: Ozone and climate stresses on vegetation (OzoNorClim).\\
  We would like to thank Greg Bodeker, Stefanie Kremser (Bodeker Scientific) and Birgit Hassler (DLR) for providing the combined vertical ozone profile database (\url{http://www.bodekerscientific.com}.
  The used Leaf Area Index (LAI) and roughness length ($Z_0$) are available online from Oak Ridge National Laboratory Distributed Active Archive Center, Oak Ridge, Tennessee, U.S.A. (\doi{10.3334/ORNLDAAC/970}).\\
  Community Emission Data System (CEDS) historical emission inventory is provided by the Joint Global Research Institute project (\url{http://www.globalchange.umd.edu/ceds/}.)
\end{acknowledgements}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%      
\section{Evaluation}
\label{sec:eval}
In this section, we present results from a manifold of OsloCTM3 model runs testing different parameters of the EMEP scheme. We focus on the change in total ozone dry deposition, ozone dry deposition velocities, and surface ozone concentration related to the stomatal conductance part of the surface resistance. We evaluate the results in the context of the multi-model comparison and observations
in\citet{ACP:Hardacre2015} (Section~\ref{subsec:model}-\ref{subsec:obs}). The OsloCTM3 is driven by meteorological input fields from \href{https://www.ecmwf.int/en/forecasts/documentation-and-support/evolution-ifs/cycle-38r1-summary-changes}{ECMWF - OpenIFS version cy38r1nc4}. CEDS historical emission inventory is used for anthropogenic emissions, while biomass burning is covered by NASA's Global Fire Emissions Database, Version4 (GFEDv4). In the following, we will discuss the various model sensitivity studies.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Sensitivity tests}
\label{subsec:sens}
A summary of specifications of all simulations discussed in this section is given in Table~\ref{tab:simsum}. For simplicity, we only list the tested parameters. An x in the table denotes that the model was run exactly in the configuration as has been decribed in Section~\ref{sec:model_des}. With respect to the sensitivity on light (PPFD), $f_\text{light}\equiv 1$ has been tested. Regarding the phenology, we have tested three different options: No phenology ($f_\text{phen}\equiv 1$), phenology including / excluding the Tropics (TR). Diverging from \citet{ACP:Simpson2012}, the simulations inititally ran with the uppermost soil water level (SWVL1). One sensitivity test was conducted using SWVL4. The meteorological year used in all simulations is 2005. Most of the simulations were run with CEDS emissions for 2014. One test has been conducted to look at the impact of the emissions.
\begin{table*}[t]
  \caption{Summary of specifications of all simulations discussed in this section. For simplicity, only the tested parameters are listed. An x denotes that the model was run exactly in the configuration as has been decribed in Section~\ref{sec:model_des}.}
  \begin{tabular}{lccccccccc}
    \tophline
    Simulation & Wesely scheme & \multicolumn{3}{c}{EMEP scheme} & \multicolumn{2}{c}{Greening season} & $v^\chem{O_3}_\text{ice/snow}$ & Forcings\\
    & & $f_\text{phen}$ & $f_\text{light}$ & $f_\text{SW}$ & SMOKE-BEIS & 5\,\unit{^\circ C}-days & (\unit{cm\,s^{-1}}) & (year)\\
    \middlehline
    Wesely type       & x & \multicolumn{3}{c}{n/a}  & x &       & 1/2000  & 2014 \\
    EMEP\_full        &   & incl. TR & x & SWLV1     & x &       & 1/2000  & 2014 \\
    EMEP\_offLight    &   & incl. TR & 1 & SWLV1     & x &       & 1/2000  & 2014 \\
    EMEP\_offPhen     &   & 1        & x & SWLV1     & x &       & 1/2000  & 2014 \\
    EMEP\_SWVL4       &   & incl. TR & x & SWLV4     & x &       & 1/2000  & 2014 \\
    EMEP\_ppgs        &   & incl. TR & x & SWLV1     &   & NH    & 1/2000  & 2014 \\
    EMEP\_ppgssh      &   & excl. TR & x & SWLV1     &   & NH+SH & 1/2000  & 2014 \\
    EMEP\_ppgssh\_ice &   & excl. TR & x & SWLV1     &   & NH+SH & 1/10000 & 2014 \\
    EMEP\_ppgs\_2005  &   & incl. TR & x & SWLV1     &   & NH    & 1/2000  & 2005 \\
    \bottomhline
  \end{tabular}
  \label{tab:simsum}
  %\belowtable{} % Table Footnotes
\end{table*}
\citep[e.g., $v^\chem{O_3}_\text{ice/snow} = 1/10000\,\unit{cm\,s^{-1}}$,][]{ACP:Helmig2007}
dry dep velocity over water \citep{JGR:Helmig2012} Impact of ocean? Although it is a low number there is 2\/3 ocean on earth... (Think, I read this in Hardacre paper... -> Luhar)

\begin{figure}[t]
  \includegraphics[width=8.3cm]{pictures/final-ozone_diff_maps}
  \caption{Relative difference between the sensitivity simulation emep\_psgsssh and the Wesely scheme in (a) surface ozone concentration; (b) ozone dry deposition velosity; (c) amount of ozone removed from the atmosphere by dry deposition.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparison with recent multi-model comparison}
\label{subsec:model}
Compare to \citet{ACP:Hardacre2015} as well as \citet{ACP:Luhar2017}. \citep{AE:Derwent2018} Uncertainties in surface ozone sources and sinks larger than in formulations? -> Need to read this one...
\begin{figure*}[t]
  \includegraphics[width=12cm]{pictures/final-total_ozone_drydep}\\
  \includegraphics[width=12cm]{pictures/final-total_ozone_drydepvelo}
  \caption{Comparison of various model runs with the OsloCTM3 and the multi-model-mean results by \citet{ACP:Hardacre2015}. (a) total annual ozone drydeposition; (b) annual average ozone dry depositon velocity.}
\end{figure*}
%
\begin{figure*}[t]
  \includegraphics[width=12cm]{pictures/final-total_ozone_drydep_hem}
  \caption{Seasonal cycle of total amount of ozone removed from the atmosphere through dry deposition seperated into northern hemisphere (NH), tropics (TR), and southern hemisphere (SH). Comparison with results from \citet{ACP:Hardacre2015}.}
\end{figure*}
%
\begin{figure}[t]
  \includegraphics[width=8.3cm]{pictures/final-total_ozone_drydep_monthly}\\
  \includegraphics[width=8.3cm]{pictures/final-total_ozone_drydepvelo_monthly}
  \caption{Comparison of monthly zonal distributions to results from \citep{ACP:Hardacre2015}. (a) Total amount of ozone removed from the atmosphere; (b) average ozone dry deposition velocitys.}
\end{figure}
%
\begin{figure}[t]
  \includegraphics[width=8.3cm]{pictures/final-total_ozone_drydepvelo_monthly_pft_nh}
  \caption{Average ozone dry deposition velocitys seperated by land use type and compared to results from \citep{ACP:Hardacre2015}.}
\end{figure}

@@

\begin{acknowledgements}
  This work was supported by the Norwegian Research Council (NRC) through the project The double punch: Ozone and climate stresses on vegetation (OzoNorClim).\\
  %We would like to thank Greg Bodeker, Stefanie Kremser (Bodeker Scientific) and Birgit Hassler (DLR) for providing the combined vertical ozone profile database (\url{http://www.bodekerscientific.com}.
  The used Leaf Area Index (LAI) and roughness length ($Z_0$) are available online from Oak Ridge National Laboratory Distributed Active Archive Center, Oak Ridge, Tennessee, U.S.A. (\doi{10.3334/ORNLDAAC/970}).\\
  Community Emission Data System (CEDS) historical emission inventory is provided by the Joint Global Research Institute project (\url{http://www.globalchange.umd.edu/ceds/}.)
  Randerson, J.T., G.R. van der Werf, L. Giglio, G.J. Collatz, and P.S. Kasibhatla. 2018. Global Fire Emissions Database, Version 4, (GFEDv4). ORNL DAAC, Oak Ridge, Tennessee, USA. https://doi.org/10.3334/ORNLDAAC/1293
\end{acknowledgements}
